---
title: "Using the Template Package"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

remotes::install_cran(c("desc"), repos = "https://cran.rstudio.com/", quiet = TRUE)
desc_obj <- desc::description$new()
package_name <- desc_obj$get_field("Package")
```

```{r setup}
```

1. Create a new repo on GitHub.
2. Use the [`git-flow`](https://blog.sourcetreeapp.com/2012/08/01/smart-branching-with-sourcetree-and-git-flow/) approach in your development cycle. 
3. Create a new release named `inception`.
4. Copy ``r package_name`` content to the new reposetory.
5. Change the ``r paste0(package_name,".Rproj")`` file to `<package-name>.Rproj`.
6. Open the `DESCRIPTION` file, and edit the following fields:
1. **Package** modify the package name while using the `tidylab.` prefix.
2. **Title** modify the package title; use uppercase words with no period ('.').
3. **URL** modify the package URL such that it leads to its GitHub repo.
4. **BugReports** edit the URL such that it leads to the package issue page.
5. **Description** modify the package decription.
7. In `README.Rmd` delete the **Useage** Section.
8. Render `README.Rmd` by clicking the **Knit** button.
9. Push changed on the `inception` branch.
10. Go to [Travis website](https://travis-ci.org/account/repositories), add the
project and enable its integration.
11. Decide if you would need binder -- an RStudio Server that lets you
demonstrate the package. If you do then:
* Uncomment *build-binder* under *.travis.yml*; and
* Uncomment *Launch Rstudio Binder* from README.Rmd.
